---
title: "Model"
author: "Jana"
date: "14/06/2022"
output: html_document
---
```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
data<-read.csv(file.choose(),header = T)
data # This dataset is about whether the school students will continue the college or not
view(data)
```
#type_school - Type of the school,the students are studied.
#school_accreditation - Grade of the school. 	
#gender - Gender of the students	
#interest - Interest of the students whether they are willing to goto the college	#residence - where the students are residing	
#parent_age - Parents  age.
#parent_salary - Parents Salary 	
#house_area - Area of the house.
#average_grades - Average Grade for the students	
#parent_was_in_college - Whether the parents studied in the college 
#in_college - whether the students are studying in the college or not

```{r}
dim(data)
#There are 1000 rows and 11 Columns
```
```{r}
str(data) # which displays the data type of the variables
```
# Numerical variables - parent_age,parent_salary,house_area,average_grades
# Categorical variables - type_school,school_accreditation,gender,interest,residence,parent_was_in_college,in_college

```{r}
barplot(table(x=data$type_school),main="Type of Schools",xlab="Schools")
# Maximum number of students studied in Academic Schools
```
```{r}
barplot(table(data$school_accreditation),
        main = "Schools Accreditation",
        xlab="Grades for Schools")
# Maximum number of students studied in a "B" grade School
```
```{r}
barplot(table(data$gender),
        main = "Male Vs Female",
        xlab = "Gender")
# There is a Maximum Number of Male students
```
```{r}
barplot(table(data$interest),
        main = "Interests for Students",
        xlab="Types of Interests")
# There is a lot of students are interested to go to college
```
```{r}
barplot(table(data$residence),
        main = "Students Residence",
        xlab = "Types of Residence ")
# There is a Lot of students from Urban Sides.
```
```{r}
hist(data$parent_age,
     main = "Age",
     xlab = "Parents Age")
# Maximum Parents Age are 50-55
# The distribution looks like Left Skew
```
```{r}
hist(data$parent_salary,
     main = "Parents Salary Details",
     xlab = "Salary")
# Maximum Parents Salaries are 4000000 - 6000000 USD Dollars
# The distribution looks like Symmetric
```
```{r}
hist(data$house_area,
     main = "Area of House",
     xlab = "Area")
# Maximum Houses areas are looks like 70 - 80 Sq.Ft(Square Feet)
# The distribution looks like Symmetric
```
```{r}
hist(data$average_grades,
     main = "Average Marks for students",
     xlab = "Marks")
# Maximum Students Average Marks is 80% 
# The distribution looks like Right skew
```
```{r}
barplot(table(data$parent_was_in_college),
        main = "Parents are Studied in College?",
        xlab = "Yes or No")
# Maximum Parents are studied in College.
```
```{r}
barplot(table(data$in_college),
        main = "How Much Students are Studying in College?",
        xlab = "Yes or No")
# 50% of Students are Studying and 50% are not Studying.
```
```{r}
table(data$interest)
boxplot(data$average_grades ~ data$interest,
        main="Interests Vs Marks",
        xlab = "Interests",
        ylab = "Marks")
# Uncertainty students have a lot of Marks
```
```{r}

boxplot(data$average_grades ~ data$school_accreditation,
        main="School Grade Vs Marks",
        xlab = "Grades",
        ylab = "Marks")
# B school Students have higher Marks than A School.
```
```{r}
boxplot(data$average_grades ~ data$residence,
        main="Residence Vs Marks",
        xlab = "Residence",
        ylab = "Marks")
# Rural students have higher marks than Urban
```
```{r}
boxplot(data$average_grades ~ data$in_college,
        main="College Students Vs Marks",
        xlab = "College Students",
        ylab = "Marks")
# College Studying Students Marks are Higher than those who didnt studied.
```
```{r}
boxplot(data$average_grades ~ data$gender,
        main="Gender Vs Marks",
        xlab = "Gender",
        ylab = "Marks")
# Both Male and Female have a Same amount of Marks
```
```{r}
boxplot(data$average_grades ~ data$parent_was_in_college,
        main="Parent Studies  Vs Marks",
        xlab = "Parent Studies",
        ylab = "Marks")
# Parents whose are studied in College, their Marks are higher than those who didn't studied.
```

```{r}
plot(data$parent_salary,data$parent_age)
# It shows there is no relationship between Parents Age and Parents Salary
```
```{r}
cor(data$parent_age,data$parent_salary)
# It ensures the relationship between Age and Salary have a Negative Correlation
```

 
 We can calculate a Marks for interested and uninterested students and we can get a insight is, there is a very small difference between interested and uninterested students.
 
So, the Councellors give some couunselling to the uninterested students for go to the college to enhance their future well.























