---
title: "Semester"
author: "Jana"
date: "27/06/2022"
output: html_document
---
```{r}
library(tidyverse)
library(ggplot2)
```
```{r}
data <- read.csv(file.choose(),header = T)
data
```
#The dataset is about a graduate school dataset.It describes about the performance of the students.

#admit - whether the student is applied for next degree.
#gre - marks of the student.
#gpa - marks in percentage.
#rank - ranks of the students.
```{r}
dim(data)
```
# There are 400 rows and 4 columns.
```{r}
head(data)

```
# Univariate Analysis - We can Visualise only one variable.
```{r}
# Histogram is used to visualise the one numeric variable
hist(data$gre,
     main = "Marks of Students",
     xlab="Marks",
     ylab="Frequency")
```
```{r}
hist(data$gpa,
     main = "Percentage of Students",
     xlab="Percentage",
     ylab="Frequency")
```
```{r}
boxplot(data$gre,
        main="Students Marks",
        ylab="Marks")
```
```{r}
boxplot(data$gpa,
        main="Students Percentage",
        ylab="GPA")
```
```{r}
boxplot(data$rank,
        main="Students Rank",
        ylab="Rank")
```
```{r}
#barplot is used to visualise the categorical variable
barplot(table(data$admit))
```
```{r}
barplot(table(data$rank))
```
# Bivariate Analysis - We can Visualise  two variables.
```{r}
# boxplot is used to visualise the one numeric variable, also used to visualise one numerical and one catogorical variable.
boxplot(data$rank ~ data$admit,
        main="Degree Applied Vs Rank",
        xlab = "Applied or not",
        ylab="Ranks")
```
```{r}
boxplot(data$gre ~ data$admit,
        main="Degree Applied Vs Marks",
        xlab = "Applied or not",
        ylab="Marks")
```
```{r}
boxplot(data$gpa ~ data$admit,
        main="Degree Applied Vs GPA",
        xlab = "Applied or not",
        ylab="GPA")
```
```{r}
#plot is used to visualise the two numerical variables
plot(gre ~ gpa,data=data)
```
```{r}
#cor is used to measure the relationship between two variables
cor(data$gre,data$gpa)
#It describes there is a positive relationship between these two variables
```
#Conclusion:
# By Analysis, we can come to know,the students those who are applied for the next degree got higher percentage then those who are not applied.

#  But, there is only a slight difference of marks between the applied and not applied students.

#   So, the Teachers encourage the students (those who are not applied for next degree) to do next degree, if they have an confusion.



















